LSOA domestic Electricty and Gas maps

### 2021-09-17 LSOA domestic Elec and Gas.Rmd
Knitting

@@

### Plotting over 65s against dom elec consumption 
```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'LSOA11CD'<- census_age$'geography code'
census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
head(census_age)
names(census_age)
message("Original Proportion Over 65:")
summary(census_age$`Proportion Over 65`)
message("New prop_65m:")
summary(census_age$prop_65m)
```
```{r Plotting elec consumption in the over 65s}
domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
Census_age_elec2019 <- merge(domelec_LSOA_2019, census_age, by = "LSOA11CD")
# select the variables we want for clarity

@@

# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = mean_dg2019)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Plotting gas usage against proportion of over 65s
```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'LSOA11CD'<- census_age$'geography code'
census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
head(census_age)
names(census_age)
message("Original Proportion Over 65:")
summary(census_age$`Proportion Over 65`)
message("New prop_65m:")
summary(census_age$prop_65m)
```
```{r Plotting gas consumption in the over 65s}
domgas_LSOA_2019$LSOA11CD <- domgas_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
Census_age_gas2019 <- merge(domgas_LSOA_2019, census_age, by = "LSOA11CD")
# select the variables we want for clarity

>>>>

```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'LSOA11CD'<- census_age$'geography code'
census_age$prop_65m <- census_age$`Over 65s`/census_age$`Age: All usual residents; measures: Value`
head(census_age)
names(census_age)
message("Original Proportion Over 65:")
summary(census_age$`Proportion Over 65`)
message("New prop_65m:")
summary(census_age$prop_65m)
```

@@

### Plotting over 65s against dom elec consumption 
```{r Plotting elec consumption in the over 65s}
domelec_LSOA_2019$LSOA11CD <- domelec_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
Census_age_elec2019 <- merge(domelec_LSOA_2019, census_age, by = "LSOA11CD")
# select the variables we want for clarity

@@

# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = mean_dg2019)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Plotting gas usage against proportion of over 65s
```{r Plotting gas consumption in the over 65s}
domgas_LSOA_2019$LSOA11CD <- domgas_LSOA_2019$`Lower Layer Super Output Area (LSOA) Code`
Census_age_gas2019 <- merge(domgas_LSOA_2019, census_age, by = "LSOA11CD")
# select the variables we want for clarity
